\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-10 doc/sui14/applications.tex
for remote control application, added info that we are using naive IR

Our prototype includes three smart devices: a lamp and a fan that could be switched on and off; a smart TV with playback, volume and navigation controls (see Figure~\ref{fig:smart-home}). The on/off appliances are using relays, and the smart TV is a 30\inch{} display connected to a laptop. User interfaces for each were pre-defined in our application.
%
We set the devices up in a simulated living room environment and invited 14 users to step through a predefined set of tasks to control the appliances at a distance.

>>>>

Our prototype \changes{(based on {\em Naive IR}\footnote{For this particular configuration, the environment is not dense enough, and {\em Naive IR} performs well for head orientation based targeting proof-of-concept.})} includes three smart devices: a lamp and a fan that could be switched on and off; a smart TV with playback, volume and navigation controls (see Figure~\ref{fig:smart-home}). The on/off appliances are using relays, and the smart TV is a 30\inch{} display connected to a laptop. User interfaces for each were pre-defined in our application.

%
We set the devices up in a simulated living room environment and invited 14 users to step through a predefined set of tasks to control the appliances at a distance.
